The ChEMBL database as Linked Open Data

### 2012-04-04 article.tex
Added draft text and references on Decision Support.

\address[A]{Department of Bioinformatics - BiGCaT, Maastricht University, ADDRESS, Maastricht,\\ The Netherlands}
\address[B]{Uppsala University}
\address[C]{University of Queensland}
\address[D]{Royal Society of Chemistry, 904 Tamaras Circle, Wake Forest, NC 27587, U.S.A.}
\address[E]{ChEBI, European Bioinformatics Institute}
\address[F]{ChEMBL, European Bioinformatics Institute}
\address[G]{Indiana University}

@@

>>>>

\address[A]{Department of Bioinformatics - BiGCaT, Maastricht University, ADDRESS, Maastricht,\\ The Netherlands}
\address[B]{Department of Pharmaceutical Biosciences, Uppsala University, PO Box 591, SE-751 24, Uppsala, Sweden}
\address[C]{University of Queensland}
\address[D]{Royal Society of Chemistry, 904 Tamaras Circle, Wake Forest, NC 27587, U.S.A.}
\address[E]{ChEBI, European Bioinformatics Institute}
\address[F]{ChEMBL, European Bioinformatics Institute}
\address[G]{Indiana University}

@@

Bioclipse Decision Support (Bioclipse DS)~\cite{Spjuth:2011uq} is a user-oriented tool for providing on-time and on-demand information on chemical structures, based on the Bioclipse workbench. Such information can include calculated properties, data from database queries, and results from predictive models. Bioclipse DS has previously been demonstrated on predictive modeling in drug safety assessment~\cite{Spjuth:2011uq} and also been linked to invoke and present results from distributed toxicity predictions from the OpenTox infrastructure~\cite{Willighagen:2011kx}.

In this study we extended Bioclipse DS with remote access to ChEMBL-RDF and Chemspider, which enables users to for chemical structures in Bioclipse look up near neighbors on Chemspider via the Chemspider Web API (SOAP) and query ChEMBL-RDF for properties regarding any measured interactions. The results are presented alongside predictive models in Bioclipse, and can be used as decision support when evaluating chemical structures and consider strategies for e.g. optimization.

[TODO: SCREENSHOT from Bioclipse-DS-ChEMBL-RDF]
